Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2021-03-11 paper/main.tex
introduction

\section{Introduction}
Nowadays, keeping track of the domestic energy usage is a common scenario in order to know how much is the real-time watt consumption. 
Anyway, in the most cases there is a sensor connected to the main safety switch giving the total energy consumption. Instead, our scenario is more accurate since we have a energy sensor for each plug connected to 220V line. In the following paragraphs, we are presenting our \textit{proof of concept} (POC) which consists of three main parts: the smart plugs, the main server and the web interface. In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consume-driven infrastructure. This latter consists of three main parts: the smart plugs, a central processing unit and the web interface. These devices are connected to the a wireless router, so is home scenario described below. It's a simple idea: let's suppose for example to plug both the dishwasher and the washing machine to two different smart plugs, and the user set up the max power consumption available for his house. On the first use of home appliances, a default value is choose in order to avoid blackout, and then we register the maximum power usage for each appliance. The user could turn on only the devices with a power consumption lower than the available watts. This is simple idea opens to possible different security issues, implementations and improvements that will be discussed in the challenges section.

>>>>

\section{Introduction}
Nowadays, keeping track of the domestic energy usage is a common scenario in domotic applications that aim to monitor the real-time watt consumption of home appliances. In most cases the solution is a sensor connected to the main safety switch yielding the total energy consumption. Our approach, to get more detailed information and to have control on the use of power by the appliances, is to have an energy sensor for each plug connected to the 220V line. In the following paragraphs, we present our \textit{proof of concept} (POC) which, functionally, consists of three main components: the smart plugs, the main server and the web interface. In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consume-driven infrastructure. This consists of: the smart plugs, a central processing unit (for the main server) and a device (for the web interface). In a home scenario these devices are connected to the home wireless router. The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level. Let's now consider a use case example: the user sets the maximum power consumption possible in the home and then turns on two appliances. When this happens for the first time the system decides, based on the type of appliance connected, a default value for the maximum power usage of the appliance. This value is then updated to reflect the real maximum power usage of the appliance. Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less then the available power. Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN. To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power on of appliances that consume more then the available power. It also gives granular information about the devices consumption and allows the user to turn on or off appliances remotely (via web interface). Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower then the real one in order to use less power or save money.
